Studying public transit API query logs\\ to get an indication of travel flows

### 2015-12-31 paper.tex
Sync

\maketitle
\begin{abstract}
% Context
%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
The iRail project hosts a route planning API for the Belgian railway company.
It is a high expresive webservice, of which the query logs are able to tell us something about the public transit demand at a certain moment.
%This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Need
In the field of urban planning, researchers need an indication of how people move between cities. 
Yet, getting indications of these travel flows has proven to be troublesome.
% Task
In this paper, we analyse the query logs of the iRail API, to see whether it can tell us something about travel flows between cities in Belgium.
% Object
We studied queries for the year 2013, which contains an average of $\sim3000$ interesting queries per day ($\sim0.4\%$ of the amount of passengers per weekday).
% Findings
Using data visualizations, we illustrate two interesting patterns that correspond to reality, as confirmed by experts, and we show one that does not.
% Conclusion
More research is needed to understand how representative for travel flows query logs may be.
% Perspectives
In earlier work, we suggested the Linked Data Fragments axis to discuss new approaches to publish queryable public transit data.
Now, we suggest a discussion for gathering query logs when using Linked Data Fragments approaches.

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=8.1cm,align=center]{histogram}
\caption{Histogram of one weekday}
\label{fig:brussels}
\end{figure}

>>>>

\maketitle
\begin{abstract}

%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
%This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Context & % Need
In the field of urban planning, researchers need an indication of how people move between cities. 
Yet, getting statistics of travel flows has proven to be troublesome.
The iRail project hosts a high expressive route planning API for the Belgian railway company.
% Task
We analyse the query logs of this API, to get an indication of travel flows between cities in Belgium.
We were able to study $\sim$100k to 500k requests for each month between October 2012 and November 2015, which amount to \todo{between $0.3\%$ and $2\%$} of the amount of monthly passengers.
% Object
Using data visualizations, we illustrate the commuting patterns in Belgium and show that Brussels, the captial, acts as a central hub. 
% Findings
The visualizations correspond to reality, as confirmed by experts. 
% Conclusion
More research is needed to understand how representative for travel flows query logs may be.
% Perspectives
In earlier work, we suggested the Linked Data Fragments axis to discuss new approaches to publish queryable public transit data.
Now, we suggest a discussion for gathering query logs when using Linked Data Fragments approaches.

@@

\begin{figure}
\centering
\includegraphics[width=193,align=center]{querylogs}
\caption{Amount of queries on the route planning part of the iRail API between 2012 and 2016. In April 2015 an official app of the Belgian railways was discontinued, which explains the sudden raise of iRail API queries.}
\label{fig:querylogs}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.3cm,align=center]{avg-all}
\caption{Distribution of iRail route planning API queries on average per day of the week between 2012 and 2016}
\label{fig:average}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=8.3cm,align=center]{dec21}
%\caption{Comparison of route planning queries on December 21st 2015 with the average on a Monday between 2012 and 2016. Whilst being a school holiday, there is no notable difference, except for the peek hours being a bit later, }
%\label{fig:dec21}
%\end{figure}

\begin{figure}
\centering
\includegraphics[width=8.3cm,align=center]{dec24}
\caption{Comparison of route planning queries on December 24th (Christmass eve) 2015 with the average on a Thursday between 2012 and 2016. The illustration shows that people started going home earlier than usual.}
\label{fig:dec24}
\end{figure}

@@
